---
title: "WRAP longitudinal assays"
output:
  html_document:
    df_print: paged
---
## Setup
### Load required libraries

```{r, message=F, warning=F}
library(tidyverse)
library(readxl)
library(janitor)
library(viridis)
library(cowplot)
library(grid)
library(lemon)
library(patchwork)
library(tcltk)

```

### Define base directories

```{r}
dir_root    <- dirname(dirname(rstudioapi::getActiveDocumentContext()$path))
dir_data    <- file.path(dir_root, "data")
dir_helpers <- file.path(dir_root, "bin", "helpers")
dir_figures <- file.path(dir_root, "figures")
dir_results <- file.path(dir_root, "results")

```

### Load helper functions

```{r}
source(file.path(dir_helpers, "generate_spaguetti_plots.R"))
source(file.path(dir_helpers, "label_analyzer_samples.R"))
```

### Files and manifests to import
```{r}
assay_files <- list.files(file.path(dir_data, "raw"), pattern = ".csv")

manifest_files <- list.files(file.path(dir_data, "raw"), pattern = ".xlsx")

```


## Import and clean data
### Match manifest ids with assay readings
```{r}

label_analyzer_samples(dir_source = file.path(dir_data, "raw"), dir_export = dir_data)

```

### Separate and clean names for analysis

```{r}



```

### Combine datasets for plotting
```{r}
data_joint_targets <- bind_rows(data_ptau217, data_gfap, data_nfl, 
                                data_ab40, data_ab42, data_ratio_ab42) 


```


## Plot results
### Define custom scales and paired comparison bar positions
```{r}
scales_y <- list(`ptau217`    = scale_y_continuous(name = "", limits = c(0, 1.7), breaks = seq(0, 1.7, 0.4)),
                 `nfl`        = scale_y_continuous(name = "", limits = c(0, 635), breaks = seq(0, 635, 150)),
                 `gfap`       = scale_y_continuous(name = "", limits = c(0, 150), breaks = seq(0, 150, 50)),
                 `ab40`       = scale_y_continuous(name = "", limits = c(0, 130), breaks = seq(0, 130, 26)),
                 `ab42`       = scale_y_continuous(name = "", limits = c(2, 10), breaks = seq(0, 10, 2.5)),
                 `ratio_4240` = scale_y_continuous(name = expression(A*beta[42]/A*beta[40]), limits = c(0.04, 0.12), breaks = seq(0, 0.2, 0.02))
                 )

scales_x <- list(`ptau217`    = scale_x_discrete(name = "", labels = c("0 hrs", "48 hrs", "72 hrs")),
                 `nfl`        = scale_x_discrete(name = "", labels = c("0 hrs", "48 hrs", "72 hrs")),
                 `gfap`       = scale_x_discrete(name = "", labels = c("0 hrs", "48 hrs", "72 hrs")),
                 `ab40`       = scale_x_discrete(name = "", labels = c("0 hrs", "48 hrs", "72 hrs")),
                 `ab42`       = scale_x_discrete(name = "", labels = c("0 hrs", "48 hrs", "72 hrs")),
                 `ratio_4240` = scale_x_discrete(name = "", labels = c("0 hrs", "48 hrs", "72 hrs"))
                 )

comparison_positions <- list(`ptau217`    = c(1, 1.2, 1.1),
                             `nfl`        = c(1, 1.2, 1.1),
                             `gfap`       = c(1, 1.2, 1.1),
                             `ab40`       = c(102, 118, 110),
                             `ab42`       = c(8, 9, 8.5),
                             `ratio_4240` = c(0.09, 0.10, 0.095))

```

### Initialize plot components
```{r}
common_y_title <- textGrob("Concentration (pg/ml)", 
                           gp  = gpar(fontsize = 9, fontfamily = "serif"), 
                           rot = 90)

common_x_title <- textGrob("Hours before freeze", 
                           gp = gpar(fontsize = 9, fontfamily = "serif"))

anova_results     <- list()
comparison_labels <- list()
target_panels     <- list()

```

### Loop around all the metrics and create individual panels
```{r}

for (i_target in 1:n_targets) {
  
  anova_results[[i_target]] <- oneway_anova(data         = filter(data_joint_targets, 
                                                                  target == target_names[i_target]),
                                            x            = hours_before_freeze, 
                                            y            = replicate_conc, 
                                            paired       = T,
                                            subject.id   = identifier,
                                            effsize.type = "eta")
  
  comparison_labels[[i_target]] <- generate_pairwise_labels(dataset = filter(data_joint_targets, 
                                                                              target == target_names[i_target]),
                                                             x      = hours_before_freeze,
                                                             y      = replicate_conc)
  
  target_panels[[i_target]] <- generate_spaguetti_plot(filter(data_joint_targets, 
                                                              target == target_names[i_target]),
                                                       response  = replicate_conc, 
                                                       font_size = 10) +
  
  scales_y[[i_target]] +
    
  scales_x[[i_target]] +
  
  facet_rep_wrap(target ~ .,
                 labeller = label_parsed) +
  
  theme(strip.background = element_rect(fill = "#680001"),
        strip.text       = element_text(color = "white", 
                                        size  = 10, 
                                        face  = "bold"))
  
  ##### Highlighting ratio plot
  if (i_target == 6) {
    
    target_panels[[i_target]] <- target_panels[[i_target]] +
      
      theme(plot.background = element_rect(colour    = "#680001", 
                                           fill      = "white", 
                                           linetype  = "dotted",
                                           linewidth = 1))
    
  }
  
  }
```

### Render panel with combined plots
```{r, fig.width=6, fig.height=5.5}
combined_panel  <- plot_grid(target_panels[[1]], target_panels[[2]], target_panels[[3]], 
                             target_panels[[4]], target_panels[[5]], target_panels[[6]],
                             labels = "AUTO",
                             label_size = 11)

final_plot <- gridExtra::grid.arrange(gridExtra::arrangeGrob(combined_panel, 
                                                             left   = common_y_title, 
                                                             bottom = common_x_title))

```

### Export plot
```{r}
ggsave(final_plot, filename = file.path(dir_figures, "assay_panel.png"), dpi = 300)

```

